Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-10-29 Article/ici_submm_cloudcorr.tex
added SI results

\documentclass[amt, manuscript]{copernicus}
%\documentclass[amt]{copernicus}

@@

\Author[1]{Inderpreet}{Kaur}
\Author[1]{Patrick}{Eriksson}
\Author[1]{Simon}{Pfreundschuh}

\affil[1]{Department of Space, Earth and Environment, Chalmers University of
  Technology, Gothenburg, Sweden}

@@

In this study, we present methodology to identify and correct the cloud impact in microwave humidity radiances. A quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to current sensor MWHS-2. With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is only partially successful in removing the cloud contamination. Though most of the cases with high cloud impact are corrected, cases with low cloud impact are only partially corrected. This is comparable to the level of accuracy achieved with operational cloud-filtering techniques. However with sub-mm channels, we are able to successfully correct most of the cases with cloud impact. The resulting error distributions are symmetric with very low spread. In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise. The methodology also works well even when only one of the higher frequencies is available. Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for most of the scenes individually. Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.

@@

The results are further compared with SI based cloud filtering. SI uses differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data:
\begin{equation}
\text{SI} = ((\text{TB}^{obs}_{90} - \text{TB}^{obs}_{150}) + (\text{TB}^{fg}_{90} - \text{TB}^{fg}_{150}))/2 
\end{equation}

where TB$^{obs}$ and TB$^{fg}$ are observation and model first guess brightness temperatures respectively.

\todo{comparsion with SI}

@@

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz. The labels ``All'' and ``Filtered(5\,K)' are as described in Table~\ref{tab:error_statistics_mwhs_14}.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{2-6}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c}{89+150\,GHz}  \\
		&	&		   &			& All & Filtered(5K)\\
		\middlehline
		Channel 11  &   bias     & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
				    &	mae      & 0.80 &   0.89 &  0.79 &  0.79  \\
					&	std      & 1.00 &   1.71 &  1.03 &  1.01  \\
					&	skewness & 0.01 & -20.18 & -0.68 & -0.45  \\
		\middlehline
		Channel 12  & bias     & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
					& mae      &  0.80 &   0.98 &  0.81 &  0.80  \\
					& std      &  1.00 &   2.26 &  1.07 &  1.05  \\
					& skewness &  0.00 & -20.72 & -0.91 & -0.70  \\
		\middlehline
		Channel 13  & bias     & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
					& mae      &  0.80 &   1.17 &  0.84 &  0.83  \\
					& std      &  1.00 &   3.04 &  1.13 &  1.10  \\
					& skewness &  0.02 & -17.85 & -1.14 & -0.98 \\		
		\middlehline
		Channel 15  & bias     & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
					& mae      &  0.80 &   1.87 &  0.97 &  0.92 \\
					& std      &  1.00 &   5.08 &  1.35 &  1.25 \\
					& skewness & -0.00 & -11.15 & -0.60 & -0.83  \\ 
		\bottomhline
	\end{tabular}
\end{table*}
In this section, we extend QRNN-single to predict NFCS values for MWHS-2 channels 11, 12, 13, and 15. The experiment QRNN-single with combination 89+150\,GHz is used and the results are displayed in  Table~\ref{tab:error_statistics_mwhs_others}.

For channel 11, the error bias after correction is only -0.03\,K in comparison to 0.16\,K before correction. The strong negative tail is also diminishes after correction, but a non-zero negative skewness indicates presence of cases with cloud impact in the corrected dataset. Filtering the cases with high cloud impact has only a marginally positive impact. A similar performance is evident for channel 12. Correction reduces the bias by to -0.05\,K and the MAE is approximately 17\% less for the entire test dataset. However the effect of partially corrected cases is evident in the negative skewness. There is again only a partial correction evident for channels 13 and 15. The bias values are quite low indicating that QRNN is successful in removing a large fraction of the cloud impact, but relatively high skewness is a consequence of cases with low cloud impact which end up with inadequate correction.

\todo{comparison with SI?}

@@

The calibration of the prediction intervals on the testing dataset is displayed in Fig~\ref{fig:calibration_mwhs}. For the entire testing dataset, the predictions are follow the y=x line, i.e. they are perfectly calibrated with the priori distribution. However for all cases with correction greater than 5\,K, the distribution is poorly calibrated. In this case, the calibration curve lies below the y=x line indicating that the prediction intervals are too narrow.

Further we analysed if the  predicted errors obtained from QRNN are representative of observed errors. Fig~\ref{fig:predicted_errors_mwhs} illustrates the predicted and observed errors for MWHS-2 channel 14. The predicted errors are slightly overestimated for negative values, but overall the predicted errors from the QRNN posterior distribution have a good match with the observed errors. It should be noted that the density plot is curtailed at $10^{-4}$. With a test dataset of 70\,000 samples, we cannot represent the far wings of the distribution accurately. The high errors which we try to estimate are rare, and can not be fully represented by QRNN.

@@

\section{Correcting cloud affected data using sub-mm frequencies}
In this section, we demonstrate that sub-mm channels can be used to formulate the cloud correction of data measured around 183\,GHz. Results from different QRNN experiments with varying input conditions are described. The results are presented in context of different sensors. Furthermore, The case specific uncertainties predicted by QRNN are also discussed.

@@

	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz. This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available. In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel. For example, for target AWS-32, the training inputs were AWS-32, AWS-41, AWS-42, AWS-43, AWS-44. QRNN was trained five times for each 183\,GHz channel as target.

\end{enumerate}

@@

\subsection{Prediction Uncertainty}
\label{sec:prediction_uncertainty}
%f 
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
	\caption{The prediction uncertainty for I2V (QRNN-single) with respect to quantiles for randomly selected 1500 cases. The quantiles have been plotted at equidistant points. The black line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
	\label{fig:prediction_uncertainty_I2V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/deviation_posterior_samples_I2V.pdf}	
	\caption{The distribution of predicted errors and observed errors for I2V as obtained from QRNN-single for the test dataset. The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
	\label{fig:predicted_errors}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
	\caption{Calibration of the prediction intervals obtained from QRNN-single for I2V. }
	\label{fig:calibration_I1V}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}
%f
\begin{figure}[t]
	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}

In order to analyse the sharpness of the predictions, the deviations of predicted quantiles from its median value are estimated. Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases. The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure for all cases. In the latter case, the uncertainty estimates would be concentrated along a narrow interval. Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value. These cases are concentrated along a narrow interval and lie close to the black curve representing a Gaussian spread. On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles. Thus QRNN is capable of capturing non-Gaussian error distributions as well.

@@

Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals on the test dataset for I1V. The predictions for the complete test dataset are well calibrated and follow the y=x line. This shows that the training and test datasets come from the same a priori distribution. On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated. In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated. The calibration curves for I2V and I3V are also similar.

Next we investigate if the uncertainty estimates given by QRNN are representative of prediction accuracy. Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the errors of best estimate binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval. For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship.

With AWS, the behaviour of predicted uncertainties was observed to be similar as for ICI (not shown). The calibration plots and the predicted errors followed the same pattern as for ICI and are not shown. However, the relation between the mean uncertainty estimate and cloud impact is displayed in Fig~\ref{fig:uncertainty_cloud_impact}. For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness. As fraction of cloud impact increases, the predictions become increasingly uncertain. The most uncertain predictions are for the lowest peaking channel AWS-32, which incidentally is also most affected by  hydrometeor impact.

@@

\subsection{Cloud correction with existing sensors}
%
The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing sensors. The methodology can correctly address the large negative values in the all-sky and clear-sky deviations, but cases with low cloud impact end up with inadequate correction. The resulting error distributions are not completely symmetric but have a low bias and spread. Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz was observed to be optimal. The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water. But using 89\,GHz along with 150\,GHz gives a slightly better performance. The channel 89\,GHz is affected by surface emissivity and is relatively less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important. We also investigated the impact of two temperature sounding channels (118....??). Both these channels provide complementary information to humidity channels in the lower troposphere. Including both these channels in the training process gave almost similar performance as with the combination 89+150\,GHz. Even though the cloud correction is partial, the performance is comparable to existing cloud filtering techniques like SI.  SI is also a partial filter which identifies the contamination only due to precipitation and cloud ice. It removes most of the cases with high departures but the resulting error distributions are asymmetric.

The partial performance of QRNN is due to incomplete orthogonal information to 183\,GHz humidity channels.  The weighting functions of window channels 89 and 150\,GHz, and the two 118\,GHz channels peak in the lower troposphere. Among these four channels, 150\,GHz has the highest peaking function around 4\,Km \cite{chen2020mwhs}. These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content beyond 2\,Km. Due to missing complementary information from other channels in the upper troposphere, QRNN fails to train to predict these cases accurately. Additional information from other channels is necessary to help QRNN train better. Among the existing channels, the overlapping weighting functions of 183\,GHz can provide additional information to train QRNN. Though these channels can help in improving the training, the non-orthogonal information introduces highly correlated observational errors. This is undesirable in data assimilation for NWP, but in future if the operational centres progress with approaches dealing correlated observation errors, using the configuration QRNN-all for cloud correction could be beneficial.

\todo{ uncertainty discussion}

\subsection{Cloud correction with sub-mm frequencies }
%
In the ICI observations examined here, the results show that using sub-mm channels can successfully predict the NFCS values with very high accuracy for I2V, and I3V. The predicted values without any filter have an excellent match with the true values, and the departures are symmetrically distributed around zero mean. Few cases with high cloud impact do affect the accuracy and introduce a small negative bias, but such cases are easily filtered out with a simple correction threshold filter. For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of noise with minimal reduction in data (2-4\%). For channel I1V, a slightly lower accuracy is observed due to relatively higher number of cases with residual cloud impact. The accuracy is improved by activating the correction filter, but some effect of residual cloud impact is apparent in the high negative skewness. Interestingly, reducing the correction threshold further has no significant effect on flagging these residual cases; in fact only the clear-sky cases are removed. This indicates that for I1V, QRNN is unsuccessful in accounting for few cases with low cloud impact. Compared to other two higher peaking channels, I1V is more sensitive to the effect of hydrometeors  and contamination from surface effects. The cases with surface contamination are also localized and seasonal. For QRNN to predict such cases accurately, QRNN should have access to complementary information from sub-mm channels. However, the weighting functions of sub-mm channels can provide only a partial coverage to the hydrometeor impact at I1V. A part of lower troposphere sensed by I1V has almost zero coverage from sub-mm channels. Though such cases are few, their lack of representation prevents QRNN from correctly learning to predict the clear-sky values accurately.

A similar pattern of results is seen for when only 325\,GHz channel is used to correct cloud impact in AWS. QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel AWS-32. For AWS-32, the resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed. This indicates that a single sub-mm channel like 325\,GHz is sufficient enough for cloud correction at 183\,GHz. This is an important result as smaller satellites are limited by their size to measure all sub-mm wavelengths.

With ICI and AWS, for some channels the variability of errors smaller than measurement noise is achieved. This is a consequence of predictions for cases which lack cloud impact. QRNN predictions are weighted mean of measurements between channels. For clear-sky conditions, multiple observations of same scene from different channels can cancel out the noise. This effect is observed to be stronger in ICI observations than AWS, due to more number of input channels while training in the former. It should be noted that with satellite measurements, the spread of error distributions smaller than noise could be difficult to achieve due to other underlying uncertainties not considered here. However, symmetric error distributions with low spread could still be extremely important from the context of data assimilation. Most of the existing cloud filtering schemes eg. \cite{buehler:aclou:07} and SI \cite{} work well only at removing cases with high cloud impact. As a consequence of the residual cloud impact, the error distributions are highly skewed. This is not the optimal solution but the best which can be achieved with present sensors. To use these observations correctly data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.

The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact. This is not unexpected as such cases form a small subset of the training set and their priori distribution is different from the entire dataset. The clear-sky cases dominate the test/training dataset, thus the a priori distribution is representative of the same. The a priori distribution of cloudy cases is different to the clear-sky cases, therefore the predictions are poorly calibrated for the former. Predictions for textit{out-of-distribution} cases is always a challenging task for deep learning algorithms and  shall always limit the performance. Improving the representation of such cases in the a priori distribution can help alleviate this problem. A larger training dataset would also be required to increase the representation of such cases in QRNN. From data assimilation perspective, information on case-specific uncertainties is extremely useful. It allows for an effective selection of weights, thus significantly improving/deteriorating the impact of measurements.

>>>>

%\documentclass[amt, manuscript]{copernicus}
\documentclass[amt]{copernicus}

@@

\Author[1]{Inderpreet}{Kaur}
\Author[1]{Patrick}{Eriksson}
\Author[1]{Simon}{Pfreundschuh}
\Author[2]{David}{Duncan}

\affil[1]{Department of Space, Earth and Environment, Chalmers University of
  Technology, Gothenburg, Sweden} 
\affil[2]{European Centre for Medium Range Weather Forecasts, Reading, UK}

@@

In this study, we present methodology to identify and correct the cloud impact in microwave humidity radiances. A channel specific quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to current sensor MWHS-2. With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is only partially successful in removing the cloud contamination. Though most of the cases with high cloud impact are corrected, cases with low cloud impact are only partially corrected. This is comparable/better to the level of accuracy achieved with operational cloud-filtering techniques, like scattering index. However with sub-mm channels, we are able to successfully correct most of the cases with cloud impact. The resulting error distributions are symmetric with very low spread. The methodology also works well even when only one of the higher frequencies is available. In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise.  Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for most of the scenes individually. Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.

\todo {write one line, why important for DA}

@@

In spite of the fact that QRNN only provides a partial cloud correction, the results are better to what scattering index (SI) based approach would give. SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data \citep{geer2015scatteringindex}. With 5\,K SI threshold, almost 30\% of the data is rejected and the error distributions have bias, mae and standard deviation as -0.23\,K 0.92\,K and 1.40\,K respectively (Table~\ref{tab:SI_statistics}).

@@

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz. The labels ``All'' and ``Filtered(5\,K)' are as described in Table~\ref{tab:error_statistics_mwhs_14}.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{2-6}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c}{89+150\,GHz}  \\
		&	&		   &			& All & Filtered(5K)\\
		\middlehline
		Channel 11  &   bias     & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
				    &	mae      & 0.80 &   0.89 &  0.79 &  0.79  \\
					&	std      & 1.00 &   1.71 &  1.03 &  1.01  \\
					&	skewness & 0.01 & -20.18 & -0.68 & -0.45  \\
		\middlehline
		Channel 12  & bias     & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
					& mae      &  0.80 &   0.98 &  0.81 &  0.80  \\
					& std      &  1.00 &   2.26 &  1.07 &  1.05  \\
					& skewness &  0.00 & -20.72 & -0.91 & -0.70  \\
		\middlehline
		Channel 13  & bias     & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
					& mae      &  0.80 &   1.17 &  0.84 &  0.83  \\
					& std      &  1.00 &   3.04 &  1.13 &  1.10  \\
					& skewness &  0.02 & -17.85 & -1.14 & -0.98 \\		
		\middlehline
		Channel 15  & bias     & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
					& mae      &  0.80 &   1.87 &  0.97 &  0.92 \\
					& std      &  1.00 &   5.08 &  1.35 &  1.25 \\
					& skewness & -0.00 & -11.15 & -0.60 & -0.83  \\ 
		\bottomhline
	\end{tabular}
\end{table*}
\begin{table}[t]
	\caption{Error statistics obtained after filtering MWHS-2 humidity observations according to scattering index.  }
	\label{tab:SI_statistics}
	\begin{tabular}{lrrrrr}
		\tophline
		& Ch. 11 & Ch. 12 & Ch. 13 & Ch. 14 & Ch. 15\\
			\cline{2-6}
		bias     & -0.05&  -0.07 & -0.14 & -0.23 &  -0.34\\
		mae      & 0.81 &   0.82 &  0.85 &  0.92 &  1.03\\
		std      & 1.02 &   1.04 &  1.10 &  1.25 &  1.53\\
		\bottomhline
	\end{tabular}
\end{table}

In this section, we extend QRNN-single to predict NFCS values for MWHS-2 channels 11, 12, 13, and 15. The experiment QRNN-single with combination 89+150\,GHz is used and the results are displayed in  Table~\ref{tab:error_statistics_mwhs_others}.

For channel 11, the error bias after correction is only -0.03\,K in comparison to 0.16\,K before correction. The strong negative tail also diminishes after correction, but a non-zero negative skewness indicates presence of cases with cloud impact in the corrected dataset. Filtering the cases with high cloud impact has only a marginally positive impact. A similar performance is evident for channel 12. Correction reduces the bias to -0.05\,K and the MAE is approximately 17\% lower for the entire test dataset. However the effect of partially corrected cases is evident in the negative skewness. There is again only a partial correction evident for channels 13 and 15. The bias values are quite low indicating that QRNN is successful in removing a large fraction of the cloud impact, but relatively high skewness is a consequence of cases with low cloud impact which end up with inadequate correction.

A comparison with SI based filtering is also made (Table~\ref{tab:SI_statistics}). For channels 11 and 12 the performance of QRNN is comparable to scattering index, albeit 30\% of the observations are rejected in the latter. For channels 13 and 15, the error statistics obtained with SI are slightly worse.

@@

The calibration of the prediction intervals on the testing dataset is displayed in Fig~\ref{fig:calibration_mwhs}. For the entire testing dataset, the predictions follow the y=x line, i.e. they are perfectly calibrated with the priori distribution. However for all cases with correction greater than 5\,K, the distribution is poorly calibrated. In this case, the calibration curve lies below the y=x line indicating that the prediction intervals are too narrow.  However since such cases are few and filtering them out results in well calibrated QRNN predictions.

Further we analysed if the  predicted errors obtained from QRNN are representative of observed errors. Fig~\ref{fig:predicted_errors_mwhs} illustrates the predicted and observed errors for MWHS-2 channel 14. The predicted errors are slightly overestimated for negative values, but overall the predicted errors from the QRNN posterior distribution have a good match with the observed errors. This is in agreement with the perfect calibration seen in Fig.~\ref{fig:calibration_mwhs}. It should be noted that the density plot is curtailed at $10^{-4}$. With a test dataset of 70\,000 samples, we cannot represent the far wings of the distribution accurately. The high errors which we try to estimate are rare, and can not be fully represented by QRNN.

@@

\section{Correcting cloud affected data using sub-mm frequencies}
In this section, we demonstrate that sub-mm channels can be used to formulate the cloud correction of data measured around 183\,GHz. Results from different QRNN experiments with varying input conditions are described. The results are presented in context of different sensors. Furthermore, the case specific uncertainties predicted by QRNN are also discussed.

@@

	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz. This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available. In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel. For example, for target AWS-32, the training inputs were AWS-32, AWS-41, AWS-42, AWS-43, AWS-44. QRNN was trained five times for each 183\,GHz channel as target. 	
\end{enumerate}

@@

\subsection{Prediction uncertainty}
\label{sec:prediction_uncertainty}
%f 
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
	\caption{The prediction uncertainty for I2V (QRNN-single) with respect to quantiles for randomly selected 1500 cases. The quantiles have been plotted at equidistant points. The red line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
	\label{fig:prediction_uncertainty_I2V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/deviation_posterior_samples_I2V.pdf}	
	\caption{The distribution of predicted errors and observed errors for I2V as obtained from QRNN-single for the test dataset. The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
	\label{fig:predicted_errors}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
	\caption{Calibration of the prediction intervals obtained from QRNN-single for I2V. }
	\label{fig:calibration_I1V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}
%f

Similar to evaluation of uncertainty estimates for MWHS-2(Sect.~\ref{sec:}), we analyse the spread of predicted quantiles, their calibration and distribution of predicted errors.

Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases. The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure for all cases. In the latter case, the uncertainty estimates would be concentrated along a narrow interval. Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value. These cases are concentrated along a narrow interval and lie close to the red line representing a Gaussian spread. On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.

Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I1V. The predictions for the complete test dataset are well calibrated and follow the y=x line. This shows that the training and test datasets come from the same a priori distribution. On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated. In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.

@@

With AWS, the behaviour of predicted uncertainties is observed to be similar as for ICI (not shown). However, the relation between the mean uncertainty estimate and cloud impact is displayed in Fig~\ref{fig:uncertainty_cloud_impact}. For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness. As fraction of cloud impact increases, the predictions become increasingly uncertain. The most uncertain predictions are for the lowest peaking channel AWS-32, which incidentally is also most affected by  hydrometeor impact.

To conclude the results, we assessed if the uncertainty estimates given by QRNN are representative of prediction accuracy. Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the errors of best estimate binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval. For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship. Similar results were also obtained with AWS(not shown).

@@

\subsection{Cloud correction with existing sensors}
%
The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing sensors. The methodology can correctly address the large negative depatures owing to cloud impact, but cases with low cloud impact end up with inadequate correction. The resulting error distributions are not completely symmetric but have a low bias and spread. Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz is observed to be optimal. The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water. But using 89\,GHz along with 150\,GHz gives a slightly better performance. The channel 89\,GHz is affected by surface emissivity and is relatively less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important. We also investigate the impact of two temperature sounding channels (MWHS-2 channel 6 and 7). Both these channels provide complementary information to humidity channels in the lower troposphere. Including both these channels in the training process had no significant effect on the prediction accuracy. We obtain almost similar performance as with the combination 89+150\,GHz.

Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI. SI is also a partial filter which identifies the contamination only due to precipitation and cloud ice. Note that SI is a one for all approach for all 183\,Ghz channels, thus is one observation is classfied as cloudy by SI, it is removed in all available humidity channels. This increases the probability of erroneously removing clear observations as cloudy. For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, with however with almost 30\% rejection rate. On the other hand, for low peaking channels, the same rejection criteria gives less accurate results than QRNN. These channels have a stronger hydrometeor impact than channels 11 and 12. Clearly, a channel specific approach like QRNN is more appropriate and gives better performance.

The partial performance of QRNN is due to incomplete orthogonal information to 183\,GHz humidity channels.  The weighting functions of window channels 89 and 150\,GHz, and the two 118\,GHz channels peak in the lower troposphere. Among these four channels, 150\,GHz has the highest peaking function around 4\,Km \cite{chen2020mwhs}. These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content beyond 2\,Km. Due to missing complementary information from other channels in the upper troposphere, QRNN fails to train to predict these cases accurately. Additional information from other channels is necessary to help QRNN train better. Among the other available channels, the overlapping weighting functions of 183\,GHz can provide additional information to train QRNN. Though these channels help in improving the training, the non-orthogonal information introduces highly correlated observational errors. This is undesirable in data assimilation for NWP, but in future if the operational centres progress with approaches dealing correlated observation errors, using the configuration QRNN-all for cloud correction could be beneficial.

The biggest advantage of using QRNN is estimation of case-specific uncertainties. The predictions over chosen quantiles quantify the underlying uncertainty. The calibration plot and distribution of predicted errors show that  QRNN predictions are able to represent the a priori distribution.  However we also observe that cases with high errors are poorly calibrated. The poor calibration predictions associated with low accuracy is a consequence of different underlying a priori distribution. Predictions with high error originate from cases with high cloud impact. Such cases have a significantly distinct a priori distribtion as compared to clear cases, which dominate the training dataset, and influence the a priori information. Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases. However such cases are rare and can be filtered out with simple threshold as showing earlier.
From data assimilation perspective, information on case-specific uncertainties is extremely useful. It allows for an effective selection of weights, thus significantly improving/deteriorating the impact of measurements.

\subsection{Cloud correction with sub-mm frequencies }
%
In the ICI observations examined here, the results show that using sub-mm channels can successfully predict the NFCS values with very high accuracy for I2V, and I3V. The predicted values without any filter have an excellent match with the true values, and the departures are symmetrically distributed around zero mean. Few cases with high cloud impact do affect the accuracy and introduce a small negative bias, but such cases are easily filtered out with a simple correction threshold filter. For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of noise with minimal reduction in data (2-4\%). For channel I1V, a slightly lower accuracy is observed due to relatively higher number of cases with residual cloud impact. The accuracy is improved by activating the correction filter, but some effect of residual cloud impact is apparent in the high negative skewness. Interestingly, reducing the correction threshold further has no significant effect on flagging these residual cases; in fact only the clear-sky cases are removed. This indicates that for I1V, QRNN is unsuccessful in correcting these cases completely. Compared to other two higher peaking channels, I1V is more sensitive to the effect of hydrometeors  and contamination from surface effects. The cases with surface contamination are also localized and seasonal. For QRNN to predict such cases accurately, QRNN should have access to complementary information from sub-mm channels. However, the weighting functions of sub-mm channels can provide only a partial coverage to the hydrometeor impact at I1V. A part of lower troposphere sensed by I1V has almost zero coverage from sub-mm channels. Though such cases are few, their lack of representation prevents QRNN from correctly learning to predict the clear-sky values accurately.

A similar pattern of results is seen for when only 325\,GHz channel is used to correct cloud impact in AWS. QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel AWS-32. For AWS-32, the resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed. This indicates that a single sub-mm channel like 325\,GHz is also sufficient enough for cloud correction at 183\,GHz. This is an important result as smaller satellites are limited by their size to measure all sub-mm wavelengths.
